### 2017-01-18 README.Rmd
updated revdep checks for this version, updated readmes, updated vignettes

[![Build Status](https://api.travis-ci.org/ropensci/taxize.png?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![codecov.io](https://codecov.io/github/ropensci/taxize/coverage.svg?branch=master)](https://codecov.io/github/ropensci/taxize?branch=master)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@

Note that a few data sources require SOAP web services, which are difficult to support in R across all operating systems. These include: World Register of Marine Species, Pan-European Species directories Infrastructure , and Mycobank, so far. Data sources that use SOAP web services have been moved to a new package called `taxizesoap`. Find it at <https://github.com/ropensci/taxizesoap>.

@@

>>>>

[![Build Status](https://travis-ci.org/ropensci/taxize.svg?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![codecov.io](https://codecov.io/github/ropensci/taxize/coverage.svg?branch=master)](https://codecov.io/github/ropensci/taxize?branch=master)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@

Note that a few data sources require SOAP web services, which are difficult to support in R across all operating systems. These include: Pan-European Species directories Infrastructure and Mycobank. Data sources that use SOAP web services have been moved to `taxizesoap` at <https://github.com/ropensci/taxizesoap>.

@@

	<td style="text-align:left;"><a href="https://services.natureserve.org/developer/index.jsp">link</a></td>
